\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-12 paper/draft.tex
Update implementation

\begin{figure*}[t]
\centering
\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
\vspace{-2mm}
\caption{
  \textbf{Example transformations.}
   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
}
\label{fig:tx2}
\vspace{-2mm}
\end{figure*}

At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:

\begin{enumerate}
% \def\labelenumi{\arabic{enumi}.}
\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
\end{enumerate}

@@

% \begin{lstlisting}[language=js,mathescape,upquote=true]
% // Node.js will wrap a module with a function,
% // so as to bring certain names into scope
% // before compiling/evaluating code.
% let wrapped = "function (" +
%         "exports, require, module, " +
%         "__filename, __dirname, CTX) {" +
%     "let Math = CTX.Math" +
%     "let console = CTX.console" +
%     //...[more definitions]
%     moduleSource +
%   "});"
% \end{lstlisting}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
\vspace{-2mm}
\caption{
  \textbf{Example transformations.}
   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
\fixme{No UX!}
}
\label{fig:tx2}
\vspace{-2mm}
\end{figure*}

This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.

In practice, the aforementioned dialysis stages can be implemented in two different ways.
The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.

With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
%   we expand on in the discussion section~\sx{reqs}.

% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.

\subsection{System Implementation}
\label{impl1}

Node.js' module system is implemented entirely in JavaScript.
It exposes \ttt{require}, a global-looking function for importing modules.
At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.

@@

% \begin{verbatim}
% let lib = `
%  function (exports, require, module,
%            __filename, __dirname, CTX) {
%    let Math = CTX.Math
%    let console = CTX.console
%    //...[more definitions]
%    ${moduleSource}
%  });`;
% \end{verbatim}
